A Mechanised Library for Generic (Co)Programming

### 2024-01-21 paper/paper.tex
small edits

As mentioned, some functions, though well-defined, cannot be accepted by the
proof assistant. One example is the quicksort algorithm. This is given by the \haskell{partition} and \haskell{quicksort} function below (written in
Haskell code):
\begin{minted}{haskell}
partition :: [a] -> ([a], a, [a])
partition (x:xs) = (filter (x <=) xs, x, filter (x >) xs)

>>>>

As mentioned, some functions, though well-defined, cannot be accepted by the
pThis specific module poses a considerable challenge for the current student cohort. However, upon evaluating their performance in assignments, I can affirm that the majority are managing well. Recognizing the need for change in the teaching methodology to foster increased engagement, I am considering shifting from traditional slides to utilising my iPad/whiteboard during lectures. Additionally, incorporating in-class group exercises aims to slow down the lecture pace and encourage active participation

The classic whiteboard teaching approach is known to enhance student involvement by compelling the lecturer to moderate their speed, allowing students to absorb the material more gradually. Supplementary materials will be provided to support their learning outside the classroom.
I intend to meticulously gauge the impact of these modifications through assignment evaluations and ongoing observation of student participation. Any deviations from the expected outcomes, indicated by a lack of in-class responses, will be promptly addressed. Encouragingly, I have already shared these proposed changes with my peers in the PGCHE, receiving positive feedback and support for the initiative.

I've already shared some of my plans with the PGCHE instructors, and the response has been quite positive. I will continue to stay in touch with them for further feedback on future changes I intend to make.
roof assistant. One example is the quicksort algorithm. This is given by the \haskell{partition} and \haskell{quicksort} function below (written in
Haskell code):
\begin{minted}{haskell}
partition :: [a] -> ([a], a, [a])
partition (x:xs) = (filter (x <=) xs, x, filter (x >) xs)
